### 2020-07-02 text/regression.tex
Remove column 1 from regression
Re #14

{\setlength{\tabcolsep}{-2pt}
{\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}\begin{tabular}{l*{4}{D{.}{.}{-1}}}\hline\hline
                    &\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
                    &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} \\
\hline
Customer-facing~workers&      -0.300\sym{**} &                     &                     &                     \\
\hspace*{1em}(share, [0,1])&     (0.116)         &                     &                     &                     \\
[1em]
\hspace*{1em}of~which~face-to-face&                     &      -0.347\sym{**} &      -0.397\sym{***}&       0.070         \\
\hspace*{1em}intensive (share, [0,1])&                     &     (0.131)         &     (0.111)         &     (0.130)         \\
[1em]
Teamwork-intensive~workers&       0.462\sym{***}&                     &                     &                     \\
\hspace*{1em}(share, [0,1])&     (0.132)         &                     &                     &                     \\
[1em]
\hspace*{1em}of~which~face-to-face&                     &      -0.282         &      -0.042         &       0.315         \\
\hspace*{1em}intensive (share, [0,1])&                     &     (0.529)         &     (0.445)         &     (0.702)         \\
[1em]
Presence-intensive~workers&       0.148         &       0.077         &      -0.071         &      -0.025         \\
\hspace*{1em}(share, [0,1])&     (0.098)         &     (0.105)         &     (0.097)         &     (0.082)         \\
[1em]
Change~in~number~of &                     &                     &       0.202\sym{***}&      -0.099         \\
\hspace*{1em}monthly visits (log)&                     &                     &     (0.057)         &     (0.096)         \\
[1em]
\hspace*{1em}$\times$~customer-facing~share&                     &                     &                     &       1.006\sym{***}\\
\hspace*{1em}([0,1])&                     &                     &                     &     (0.319)         \\
[1em]
\hspace*{1em}$\times$~teamwork-intensive~share&                     &                     &                     &       0.351         \\
\hspace*{1em}([0,1])&                     &                     &                     &     (1.097)         \\
\hline
Observations        &          79         &          79         &          78         &          78         \\
\(R^{2}\)           &       0.221         &       0.200         &       0.383         &       0.555         \\
\hline\hline
\end{tabular}
}

>>>>

{\setlength{\tabcolsep}{-2pt}
{\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}\begin{tabular}{l*{4}{D{.}{.}{-1}}}\hline\hline
                    &\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}\\
                    &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} &\multicolumn{1}{c}{} \\
\hline
Customer-facing~workers&      -0.418\sym{**} &      -0.463\sym{***}&       0.012         \\
\hspace*{1em}(share, [0,1])&     (0.164)         &     (0.152)         &     (0.173)         \\
[1em]
Teamwork-intensive~workers&       0.024         &       0.254         &       0.600         \\
\hspace*{1em}(share, [0,1])&     (0.563)         &     (0.532)         &     (0.839)         \\
[1em]
Presence-intensive~workers&       0.079         &      -0.051         &      -0.005         \\
\hspace*{1em}(share, [0,1])&     (0.125)         &     (0.136)         &     (0.113)         \\
[1em]
Change~in~number~of &                     &       0.185\sym{***}&      -0.119         \\
\hspace*{1em}monthly visits (log)&                     &     (0.063)         &     (0.131)         \\
[1em]
\hspace*{1em}$\times$~customer-facing~share&                     &                     &       1.021\sym{**} \\
\hspace*{1em}([0,1])&                     &                     &     (0.447)         \\
[1em]
\hspace*{1em}$\times$~teamwork-intensive~share&                     &                     &       0.332         \\
\hspace*{1em}([0,1])&                     &                     &     (1.500)         \\
\hline
Observations        &          79         &          78         &          78         \\
\(R^{2}\)           &       0.187         &       0.302         &       0.435         \\
\hline\hline
\end{tabular}
}
